Tweedie in TMB

### 2019-02-20 analysis/tweedie-TMB.Rmd
tidy tweedie TMB

## Make C++ file
# TMB::template("tweedie_tmb.cpp")
## Compile and load the model
compile("tweedie_tmb.cpp")
dyn.load(dynlib("tweedie_tmb"))
```

Simulate data

@@

@@

## Get parameter uncertainties and convergence diagnostics
sdr <- sdreport(obj)
sdr
```

# find maximum likelihood using nlminb

@@

# check both methods against values are returned with glm
```{r}
tweedie_glm <- glm(y ~ x, family = tweedie(var.power = 1.5, link.power = 0))
summary(tweedie_glm)
coef(tweedie_glm)
sdr
tweedie_ml$par 
```

>>>>

## Make C++ file
# TMB::template("tweedie_tmb.cpp")
## Compile and load the model
compile("src/tweedie_tmb.cpp")
dyn.load(dynlib("src/tweedie_tmb"))
```

# Simulate data

@@

# Send data to TMB function to get likelihood profiles for parameters

@@

## Get parameter uncertainties and convergence diagnostics
sdr <- sdreport(obj)
sdr

## Get likelihood profiles for individual parameters:
a_profile <- tmbprofile(obj, "a")
b_profile <- tmbprofile(obj, "b")
confint(a_profile)
confint(b_profile)

plot(a_profile)
plot(b_profile)

```

# For comparision, find maximum likelihood parameter estimates using nlminb

@@

# Check both methods against values are returned with a glm

```{r}
tweedie_glm <- glm(y ~ x, family = tweedie(var.power = 1.5, link.power = 0))
summary(tweedie_glm)
coef(tweedie_glm)
sdr$par.fixed
tweedie_ml$par 
```
